\section{Conclusion}
\label{sec:conclusion}
Schubert closed his 2007 note wondering whether h\textsubscript{2} of institutes would prove more interesting than h\textsubscript{2} of journals, absent the researcher--institute--country data needed to check. Nineteen years and 17.1 million OpenAlex authors later, the answer is yes, but not in the way a single top-10 table would suggest.

The overall h\textsubscript{2} ranking is the least interesting object in this paper. Because Medicine alone accounts for 44\% of the author pool, the unrestricted university-wide aggregate is, in substance, a ranking of medical school size. The field decomposition reveals a completely different map of global research strength: Wageningen leads Agricultural \& Biological Sciences and Environmental Science globally while ranking 172nd overall; Carnegie Mellon leads Computer Science from 175th; the University of Science and Technology of China sweeps Materials Science, Engineering, and Energy from 39th; and Shenyang Pharmaceutical University leads Pharmacology from 535th. Brazil offers perhaps the sharpest illustration of what the overall ranking hides: the Universidade de S\~{a}o Paulo and the Universidade Estadual de Campinas hold two of the world's six deepest dental-research benches despite neither country nor either institution appearing anywhere near the top of any general-purpose ranking. The field-level h\textsubscript{2} is the unit that should be the default for comparison, not the aggregate.

The Academic Olympics is the most readable summary of the country-level results. The United States wins 22 of 26 golds. China's five represent a focused push in applied and materials science; there are no Chinese medals in arts, humanities, social sciences, or business. The United Kingdom places in the top three in nearly every field (10 silvers, 9 bronzes) and tops none of them. Italy and Japan both reach h\textsubscript{3} $\approx$ 45--46 while differing 6$\times$ in institutional scale (229 versus 1{,}358 institutions); the raw ranking puts them adjacent, and the efficiency metric pulls them apart.

On the methodological side, Egghe's power-law functional form is empirically well-supported: institution count alone explains 91--92\% of the variance in h\textsubscript{2} and h\textsubscript{3} respectively. However, the theoretical compounding prediction $\alpha_0\alpha_1 \approx \beta_1$ fails by 177\%. % The source of the discrepancy is that the discrete MLE tail fits locate $x_\mathrm{min}$ far above unity and describe the extreme upper tail, not the global Lotka parameter Egghe's derivation requires.
The model is empirically useful; the underlying theory needs a different reading.

Several limitations constrain interpretation. Author disambiguation is the most consequential open problem: the four outlier cases identified in cross-validation (notably Lei Jiang, $\mathrm{h}_1^\mathrm{OpenAlex} = 215$ against Web of Science $= 115$) confirm that merger errors cluster in non-Anglophone and common-name strata, exactly the authors whose inflated h\textsubscript{1} values would propagate most damagingly into institutional and country-level rankings. Arts and Humanities are systematically under-covered in all major citation databases: both threshold authors sampled at Oxford returned no value in Web of Science, Scopus, or Google Scholar, and h-index comparisons in book-based fields should be read with correspondingly less confidence. OpenAlex's inconsistent retraction flagging leaves a small, unquantified fraction of h\textsubscript{1} values potentially inflated. Saudi Arabia's efficiency rank (4th, $\varepsilon_3 = 6.69$) is plausibly an artifact of affiliation-listing for funding rather than resident research presence~\citep{saudi}, a data-quality distortion visible in the output but not removable without ground-truth affiliation data. Finally, h\textsubscript{2} is not comparable across fields of different size: Decision Sciences (max h\textsubscript{2} $= 22$) cannot be placed on the same scale as Medicine (max h\textsubscript{2} $= 119$), and the results should be read within fields only.

The most impactful near-term improvement to this framework would require a data source that does not yet exist: departmental affiliation in OpenAlex. If OpenAlex were to record the department within an institution alongside the institution itself, the hierarchy would extend naturally to researcher $\to$ department $\to$ institution $\to$ country, with successive indices h\textsubscript{1} through h\textsubscript{4}. Departments are field-specialized by construction, so the step of inferring each author's modal field from topic weights may become unnecessary at the departmental level. I flag this as the single most valuable addition OpenAlex could make for scientometric work of this kind.